exp108 - g_l sensitivity analysis.

### 2019-06-19 voltagebudget/analysis/exp108_analysis.Rmd
WIP

---
title: "Sweep A - general experiment analysis."
output: html_notebook
---

@@

```{r, message=FALSE}
exp <- "106"
g_ls <- c("10e-9", "12e-9", "14e-9", "16e-9")

@@

# -
rm(df, exp, g_l, g_ls, name)
```

@@

# Ratio ests
```{r, fig.width=1}
ratios <- NULL
for (V in c("10e-9", "12e-9", "14e-9")) {
  tmp <- filter(results, g_l == V, N == 1, V_osc/V_comp < 5)
  pnts <- find_point(normalize(tmp$errors_pop), tmp$V_osc/tmp$V_comp, 0.5)  
  row <- c(pnts, as.numeric(V))
  ratios <- rbind(ratios, row)
}
ratios <- as.data.frame(ratios, stringsAsFactors=FALSE)
colnames(ratios) <- c("error_50", "ratio", "g_l")
# Get ratio

ratios %>% 
  ggplot(aes(x=g_l*1e9, ratio)) + 
  geom_point() + 
  theme_classic()
```

>>>>

---
title: "exp108 - g_l sensitivity analysis."
output: html_notebook
---

@@

```{r, message=FALSE}
exp <- "108"
g_ls <- c("1.0e-08", "1.05e-08", "1.1e-08", "1.15e-08", "1.2e-08")

@@

# -
# rm(df, exp, g_l, g_ls, name)
```

@@

# Ratio ests
```{r, fig.width=1}
ratios <- NULL
for (V in g_ls) {
  tmp <- filter(results, g_l == V, N == 1, V_osc/V_comp < 5)
  pnts <- find_point(normalize(tmp$errors_pop), tmp$V_osc/tmp$V_comp, 0.5)  
  row <- c(pnts, as.numeric(V))
  ratios <- rbind(ratios, row)
}
ratios <- as.data.frame(ratios, stringsAsFactors=FALSE)
colnames(ratios) <- c("error_50", "ratio", "g_l")
# Get ratio

ratios %>% 
  ggplot(aes(x=g_l*1e9, ratio)) + 
  geom_point() + 
  theme_classic() +
  ylim(0, 1)
```
